### 2017-11-09 Graduate - Introduction to Analysis I/Assignment 7/7-Homework20171108.tex
update

\smallskip
\textbf{Solution:}
\smallskip

\item  Problem 10, Chapter 6
\item  Problem 13, Chapter 6

@@

\item  Problem 16, Chapter 6

>>>>

\smallskip
\textbf{Solution:}
\smallskip
Sufficiency. First, we show $\{I_k\}$ is a Vitali cover of $E$. Otherwise, there exists $x\in E, ~\epsilon > 0$, s.t. for each $I_k $ for which $x\in I_k $, $m(I_k) > \epsilon$. Then
$$\sum_{k=1}^{\infty}m(I_k) \ge \sum_{x\in I_k}m(I_k) \ge \sum\limits_{x\in I_k}\epsilon = \infty
$$
since $x$ belongs to infinity many of $I_k $. This makes a contradiction with the assumptions.

By Problem 6.6 we know Vitali Covering Lemma holds for general nondegenerate intervals, then

\bigskip
\item  Problem 10, Chapter 6
\item  Problem 13, Chapter 6

@@

\bigskip
\item  Problem 16, Chapter 6
